The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-06-10 manuscript/5pillars.Rmd
Add documentation and missing references for Software Heritage

Although DVCSs assist with code sharing, they are not considered a long-term archiving solution,
as recalled by the complete shutdown of the Google Code platform in 2015
and the end of Mercurial support by the Bitbucket platform in 2020.
The code needs to be deposited to a long-term repository.
[Zenodo](https://zenodo.org/) and [Figshare](https://figshare.com/) are often used
to store the content of a repository but do not retain the history of the development of the source code.
[Software Heritage](https://www.softwareheritage.org/) @dicosmo2017 is the universal software archive
whose mission is to collect, preserve and share source code. Software Heritage provides
an intrinsic persistent identifier called SWHID that allows to cite the archived source code
in the respective journal article/preprint. The archival of the source code in Software Heritage
can be performed manually or automated by a webhook within a continuous integration.

>>>>

Although DVCSs assist with code sharing, they are not considered a long-term archiving solution,
as recalled by the complete shutdown of the Google Code platform in 2015
and the end of Mercurial support by the Bitbucket platform in 2020.
The code needs to be deposited to a long-term repository.
[Zenodo](https://zenodo.org/) and [Figshare](https://figshare.com/) are often used
to store the content of a repository but do not retain the history of the development of the source code.
[Software Heritage](https://www.softwareheritage.org/) [@dicosmo2017; abramatic2018] is the universal software archive
whose mission is to collect, preserve and share source code. Software Heritage provides
an intrinsic persistent identifier called SWHID that allows to cite the archived source code
in the respective journal article/preprint [@cosmo2020]. The archival of the source code in Software Heritage
can be performed [manually](https://archive.softwareheritage.org/save/) 
or automated by a [webhook](https://docs.softwareheritage.org/user/save_code_now/webhooks/index.html) 
within continuous integration.
